sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-09-12 doc/paper-jss/paper-jss.Rmd
Fixes

```{r pcod-eg1-sanity, eval=TRUE, echo=TRUE, message=FALSE}
sanity(fit)
```

@@

As a second example, we will construct a spatiotemporal model of catch rates of
Pacific Spiny Dogfish (*Squalus suckleyi*) from a trawl survey off the west
coast of Vancouver Island, Canada. This example extends the spatial model
described above by also including (1) spatiotemporal fields allowing the
distribution in each year to be unique, (2) a time-varying intercept as an
AR(1) process to allow year effects to vary but remain autocorrelated, (3)
a smooth effect of depth, allowing catch rates to vary non-linearly with
depth, and (4) spatial anisotropy allowing spatial correlation to be directionally
dependent. Since catch rates are positive, continuous, and contain zeros, we begin
by specifying the response family as a Tweedie distribution [@tweedie1984] with
a log link. We then compare alternative families, spatiotemporal random field
structures, and the inclusion of anisotropy to illustrate the flexibility of
\pkg{sdmTMB}.

@@

```{r dog-head-dat, echo=TRUE}
dat <- select(dogfish, longitude, latitude, year, 
  catch_weight, area_swept, depth)
head(dat, n = 3)
```

>>>>

```{r pcod-eg1-sanity, eval=TRUE, echo=TRUE, message=FALSE}
sanity(fit_bin_rf)
```

@@

As a second example, we will construct a spatiotemporal model of catch rates of
Pacific Spiny Dogfish (*Squalus suckleyi*) from a trawl survey off the west
coast of Vancouver Island, Canada. This example extends the spatial model
described above by also including (1) spatiotemporal fields allowing the
distribution in each year to be unique, (2) a time-varying intercept as an
AR(1) process to allow year effects to vary but remain autocorrelated, (3)
a smooth effect of depth, allowing catch rates to vary non-linearly with
depth, and (4) spatial anisotropy allowing spatial correlation to be directionally
dependent. Since catch rates are positive, continuous, and contain zeros, we begin
by specifying the response family as a Tweedie distribution [@tweedie1984] with
a log link. We then compare alternative families, spatiotemporal random field
structures, and the exclusion of anisotropy to illustrate the flexibility of
\pkg{sdmTMB}.

@@

```{r dog-head-dat, echo=TRUE}
dat <- select(dogfish, longitude, latitude, year, 
  catch_weight, area_swept, depth) |> as_tibble()
head(dat, n = 3)
```
